Pretty darn good control: when are approximate solutions better than approximate models

### 2023-06-22 manuscript/manuscript.Rmd
added table of models

\textbf{The Environment.}
As seen in Fig. **TBD CONCEPTUAL**, we consider four different models of the ecosystem with which the fishery interacts, each of this is called an *environment*, alluding to the environment in an RL setting.
To recap, these four environments are a single-species growth model \eqref{eq:may} for a harvested species; a three-species model \eqref{eq:3d model stoch} with a single harvested species; the same three-species model but with *two* harvested species; and, finally, a three-species model with a time-varying parameter and two harvested species.

The policies explored were functions from states $N_t$ to either a single number $M_X(N_t) = \pi(N_t)$, or a pair of numbers $(M_X(N_t), M_Y(N_t)) = \pi(N_t)$ depending on the environment considered.
\textbf{Probably a table showing the different combinations of species and fishery numbers would be good, possibly giving these ‘scenarios’ names.}

>>>>

\textbf{The Environment.}
As seen in Fig. **TBD CONCEPTUAL**, we consider four different models of the ecosystem with which the fishery interacts, each of this is called an *environment*, alluding to the environment in an RL setting.
We summarize these models in Table \ref{tab:models}.
To recap, these four environments are a single-species growth model \eqref{eq:may} for a harvested species; a three-species model \eqref{eq:3d model stoch} with a single harvested species; the same three-species model but with *two* harvested species; and, finally, a three-species model with a time-varying parameter and two harvested species.

The policies explored were functions from states $N_t$ to either a single number $M_X(N_t) = \pi(N_t)$, or a pair of numbers $(M_X(N_t), M_Y(N_t)) = \pi(N_t)$ depending on the environment considered.

\begin{table}
  \begin{center}
    \begin{tabular}{|l|c|c|c|c|}
      \hline
      \textbf{Model name} & \textbf{Model eqs.} & \textbf{N. Sp.} & \textbf{Harv. Sp.} & \textbf{Stationary?}\\
      \hline
      1 species, 1 fishery & \eqref{eq:may} & 1 & $X$ & Yes \\
      3 species, 1 fishery & \eqref{eq:3d model} & 3 & $X$ & Yes \\
      3 species, 2 fishery & \eqref{eq:3d model} & 3 & $X$ and $Y$ & Yes \\
      3 species, 2 fishery, time-varying parameters & \eqref{eq:3d model} & 3 & $X$ and $Y$ & No \\
      \hline
    \end{tabular}
    \caption{Table of models considered in this paper. Here, \textbf{N. Sp.} is the \emph{number of species} in the model, \textbf{Harve. Sp.} is the species of the model which are harvested, and \textbf{Stationary?} refers to whether the parameters of the model have fixed values (or, on the contrary, if they vary in time). The only non-stationary case presented in the paper is where $r_X$ drifts linearly with time. In the code repository associated to the paper, we consider other possible choices of non-stationarity.}
    \label{tab:models}
  \end{center}
\end{table}
